### 2013-06-08 doc/pgas13/relatedwork.tex
Ah, that's how Treiber is spelled...

\section{Related Work}
Attempts to improve the scalability of synchronized data structures are as old as the data structures themselves. Though much attention has gone to lock-free data structures such as the Trieber Stack~\cite{trieber} and Michael-Scott Queue~\cite{msqueue}, a good body of work has explored ways of scaling globally-locked data structures.

>>>>

\section{Related Work}
Attempts to improve the scalability of synchronized data structures are as old as the data structures themselves. Though much attention has gone to lock-free data structures such as the Trieber Stack~\cite{treiber} and Michael-Scott Queue~\cite{msqueue}, a good body of work has explored ways of scaling globally-locked data structures.
